\documentclass[10pt,letterpaper]{extarticle}

% ----------------------------------------------------------------------
%  PACKAGES
% ----------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scaled=0.96]{helvet}        % clean Helvetica/Arial-style sans-serif
\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=0.5in,bottom=0.5in,left=0.6in,right=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

% ----------------------------------------------------------------------
%  COLOURS
% ----------------------------------------------------------------------
\definecolor{ink}{HTML}{1A1A1A}
\definecolor{accent}{HTML}{1F3B5B}
\definecolor{muted}{HTML}{5A5A5A}
\definecolor{rule}{HTML}{C9D2DC}

\color{ink}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ----------------------------------------------------------------------
%  LAYOUT
% ----------------------------------------------------------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1.03}
\pagestyle{empty}

\setlist[itemize]{leftmargin=1.15em, topsep=2pt, partopsep=0pt, itemsep=1.8pt, parsep=0pt, label=\textcolor{accent}{\small\textbullet}}

\titleformat{\section}
  {\color{accent}\bfseries\fontsize{11.5}{13}\selectfont}
  {}{0pt}{}[\vspace{1.5pt}{\color{rule}\titlerule[1.1pt]}\vspace{3pt}]
\titlespacing*{\section}{0pt}{7pt}{0pt}

% ----------------------------------------------------------------------
%  ENTRY MACROS
% ----------------------------------------------------------------------
\newcommand{\entry}[2]{%
  \vspace{2.5pt}%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{#1} & {\color{muted}\small #2}\\
  \end{tabular*}\par\vspace{-1pt}%
}
\newcommand{\meta}[1]{{\color{muted}\small #1}\par\vspace{1pt}}

% ======================================================================
\begin{document}

% ---------------------------- HEADER ----------------------------------
\begin{center}
  {\color{accent}\fontsize{20}{23}\selectfont\bfseries Yuvraj Sehgal}\\[3pt]
  {\small
   St.\ Catharines, ON, Canada
   \;\textbullet\; 437-335-5700
   \;\textbullet\; \href{mailto:17yuvraj.sehgal@gmail.com}{17yuvraj.sehgal@gmail.com}}\\[2pt]
  {\small
   \href{https://github.com/17YuvrajSehgal}{github.com/17YuvrajSehgal}
   \;\textbullet\; \href{https://www.linkedin.com/in/yuvraj-sehgal/}{linkedin.com/in/yuvraj-sehgal}
   \;\textbullet\; \href{https://17yuvrajsehgal.github.io/Yuvraj-Portfolio-Website/}{Portfolio}}
\end{center}

\vspace{-2pt}

% ---------------------------- SUMMARY ---------------------------------
{\small
Computer Science MSc researcher and software engineer with 2+ years of production experience across AI services, full-stack development, data pipelines, and QA automation at Scotiabank and Mengalo. Sole recipient of the Match of Minds research scholarship and author of two peer-reviewed papers (FSE, JSS) on machine learning for systems. Specializes in AI/ML (deep learning, NLP, LLM/RAG), data-intensive backends, and reliable automation with Python, SQL, and cloud infrastructure.}

% --------------------------- SKILLS -----------------------------------
\section{Technical Skills}
{\small
\textbf{Languages:} Python, Java, SQL, JavaScript/TypeScript, Go, Bash\\
\textbf{AI \& ML:} PyTorch, TensorFlow, scikit-learn, Hugging Face, deep learning, NLP, LLM fine-tuning, prompt engineering, LangChain, LangGraph, RAG\\
\textbf{Data \& Analytics:} ETL/ELT, dimensional modeling, dbt, Databricks, Apache Airflow, Apache Spark, Pandas, NumPy, MapReduce, data warehousing\\
\textbf{Databases:} PostgreSQL, AlloyDB, MongoDB, Firestore, Neo4j (knowledge graphs)\\
\textbf{Cloud \& DevOps:} GCP (Cloud Run, Compute Engine), Docker, Kubernetes, Terraform, CI/CD (Jenkins, Git, Bitbucket)\\
\textbf{Web \& Testing:} React, Node.js, FastAPI, Spring Boot, REST APIs, Selenium, Appium, RestAssured, Cucumber/BDD, JUnit, Jest, OpenTelemetry}

% --------------------------- EDUCATION --------------------------------
\section{Education}

\entry{M.Sc.\ Computer Science \textnormal{\textbar} Brock University}{Sept 2025 -- Sept 2027 (expected)}
\meta{Thesis-based; research in AI for systems and trustworthy, responsible AI. \,\textbar\, St.\ Catharines, ON}

\entry{B.Sc.\ (Honours) Computer Science, Intelligent Systems \textnormal{\textbar} Brock University}{Jan 2021 -- Jan 2025}
\meta{GPA 87/100 \,\textbar\, Dean's Honour List (all years) \,\textbar\, Golden Key International Honour Society}

% ------------------------- EXPERIENCE ---------------------------------
\section{Experience}

\entry{Artificial Intelligence Researcher \textnormal{\textbar} Brock University}{Feb 2026 -- Present}
\meta{Mitacs Accelerate industrial fellowship with Ciena Corp. \,\textbar\, St.\ Catharines, ON}
\begin{itemize}
  \item \textbf{TraceSynth}: developed constraint-guided diffusion models that generate production-quality Linux kernel traces; published at \textit{FSE 2026 (Industry Track)}.
  \item \textbf{LMAT}: contributed to an adaptive tracing approach for efficient system-behavior analysis using language models; published in the \textit{Journal of Systems and Software (2026)}.
  \item Built an agentic incident-triage system (LangGraph + hypothesis-driven ReAct loop) correlating logs, telemetry, and historical Jira data for automated root-cause diagnosis.
  \item Curated large-scale microservice trace/log datasets from benchmark systems (DeathStarBench, TrainTicket) on GCP for AIOps research.
\end{itemize}

\entry{AI Developer \textnormal{\textbar} Mengalo}{Aug 2024 -- Dec 2025}
\meta{Canada}
\begin{itemize}
  \item Built and deployed production AI services and REST APIs (Python, FastAPI) on Docker and GCP for business and customer-engagement automation.
  \item Designed an LLM- and RAG-powered analytics chatbot (LangChain, Neo4j) for real-time, natural-language querying over operational data.
  \item Implemented NLP, prompt-engineering, and knowledge-graph extraction pipelines to drive innovation across teams.
\end{itemize}

\entry{Research Assistant \textnormal{\textbar} Brock University}{Jan 2024 -- Jan 2025}
\meta{St.\ Catharines, ON}
\begin{itemize}
  \item Built an artifact-documentation tool (Python OOP, OpenAI API, Neo4j) that analyzes conference acceptance probabilities and cut documentation time by $\sim$90\%.
  \item Created an open-source dataset of 2{,}000+ research artifacts across 40 conferences (projected $\sim$30\% research-efficiency gain); sole departmental recipient of the Match of Minds scholarship.
\end{itemize}

\entry{QA Automation Engineer \textnormal{\textbar} Scotiabank}{May -- Aug 2024}
\meta{Toronto, ON}
\begin{itemize}
  \item Built Android test automation for 15+ scenarios (Java, Selenium, Appium), cutting testing time by over 75\% for financial applications.
  \item Developed API automation libraries (Selenium, RestAssured) and HTML/CSS reporting, cutting validation time $\sim$50\%.
\end{itemize}

\entry{Full Stack Developer \textnormal{\textbar} Scotiabank}{May -- Aug 2023}
\meta{Toronto, ON}
\begin{itemize}
  \item Engineered Python ETL/data pipelines to ingest, transform, validate, and reconcile operational data feeds, cutting manual file handling by 20\% and improving data reliability and reproducibility.
  \item Migrated and transformed up to 350 billion rows of data from Databricks to AlloyDB through large-scale data pipelines, improving query performance by 10x.
  \item Built the bank's LMS platform with a responsive ReactJS frontend and Node.js/REST backend microservices, deployed to GCP Cloud Run with Firestore persistence.
  \item Delivered a JUnit/Jest/React Testing Library test suite, raising coverage 15\% to meet the bank's 85\% mandate.
\end{itemize}

\entry{QA Automation Engineer \textnormal{\textbar} Scotiabank}{Sept -- Dec 2022}
\meta{Toronto, ON}
\begin{itemize}
  \item Automated 35+ regression scenarios for front-office financial systems (Selenium, Cucumber BDD, Java), reducing manual testing effort $\sim$70\%.
  \item Integrated suites into CI/CD with Jenkins, Git, and Bitbucket for automated deployments and code review.
\end{itemize}

% ------------------------- PUBLICATIONS -------------------------------
\section{Publications}
{\small
\textbf{Y. Sehgal}, S. Patel, M. Panahandeh, N. Ezzati-Jivan, F. Tetreault. \enspace TraceSynth: Generating Production-Quality Kernel Traces with Constraint-Guided Diffusion Models. \textit{FSE Companion '26 (Industry Track), ACM, pp.\ 496--506.}\\
{\color{muted}\href{https://doi.org/10.1145/3803437.3805222}{doi.org/10.1145/3803437.3805222}}\\[2.5pt]
K. Darvishi, M. Noferesti, \textbf{Y. Sehgal}, N. Ezzati-Jivan. \enspace LMAT: An Adaptive Tracing Approach Based on Efficient System Behavior Analysis Using Language Models. \textit{Journal of Systems and Software, vol.\ 238, art.\ 112890, Elsevier, 2026.}\\
{\color{muted}\href{https://doi.org/10.1016/j.jss.2026.112890}{doi.org/10.1016/j.jss.2026.112890}}}

% ------------------- CERTIFICATIONS + ADDITIONAL ----------------------
\section{Certifications \& Additional}
{\small
\textbf{Certifications:} OAuth2 \& OpenID Connect \,\textbullet\, Java EE: Servlets \& JSP \,\textbullet\, SSL Certificates for Web Developers \,\textbullet\, Maven Fundamentals \,\textbullet\, Unit Testing with Jasmine\\[2pt]
\textbf{Awards:} Mitacs Accelerate Fellowship (Ciena, \$10K) \,\textbullet\, Graduate Research Funding (\$29{,}348) \,\textbullet\, Match of Minds Scholarship (sole departmental recipient) \,\textbullet\, Golden Key (top 15\%) \,\textbullet\, Brock Entrance Scholarship (\$6K)\\[2pt]
\textbf{Also:} TA --- COSC 3P97 Mobile Computing \& 3P95 Software Analysis \& Testing (2025--26) \,\textbullet\, Indian citizen w/ Canadian study permit \,\textbullet\, English, Hindi.}

\end{document}